---
title: "Suggestion Confidence A/B Test Initial Analysis"
author: "Mikhail Popov"
date: "August 11, 2015"
output:
  html_document:
    highlight: espresso
    keep_md: yes
    theme: united
    toc: yes
    toc_depth: 4
---

## Packages Used In Analysis

```{r}
# install.packages('ggthemes', dependencies = TRUE) # for theme_fivethirtyeight
# install.packages('import') # for importing specific functions from packages
c("magrittr", "tidyr", "knitr", "ggplot2", "ggthemes") %>%
  sapply(library, character.only = TRUE) %>% invisible
import::from(dplyr, select, arrange, rename, mutate, summarise, keep_where = filter)
```

```{r, echo = FALSE}
# Data Import
load("initial_analysis/ab_test_initial_data.RData")
data$zero_results <- factor(data$results, c(FALSE, TRUE), c("Yes", "No"))
data$results <- factor(data$results, c(TRUE, FALSE), c("Yes", "No"))
data$test_group <- factor(data$test_group)
data$project <- factor(data$project)
data$source <- factor(data$project)
data$country <- factor(data$country)
data$browser <- factor(data$browser)
data$class <- factor(data$class)
```

## Data Cleanup

Oliver has taken care of parsing the log files from JSON-y format to a tabular one. He has also mapped IP addresses to country codes and parsed the user agents and tagged known automata. He also noticed that the IP address **85.13.134.246** from Germany is an abusive spider responsible for 2.1 million of the observations. We are excluding this user from analysis.

```{r}
data <- keep_where(data, ip != "85.13.134.246")
```

## Summary Statistics

```{r}
mosaicplot(zero_results ~ test_group, data = data, shade = TRUE,
           main = "Association of test group and zero results",
           xlab = "Got zero results", ylab = "Test group")
```

```{r, echo = FALSE}
chisq_test_results <- with(data, {
  chisq.test(x = test_group, y = zero_results, correct = FALSE)
}) # chisq_test_results$stdres
```

When we look at the standardized residuals (shown in the mosaic plot above), we see that (very slightly) less users would have gotten ...

|   |       Yes|        No|
|:--|---------:|---------:|
|a  |  2.684949| -2.684949|
|b  | -2.684949|  2.684949|

```{r}
par(mfrow = c(1, 2))
mosaicplot(zero_results ~ test_group, data = keep_where(data, class != "Spider"),
           shade = TRUE, sub = "(Actual users)",
           main = "Association of test group and zero results",
           xlab = "Got zero results", ylab = "Test group")
mosaicplot(zero_results ~ test_group, data = keep_where(data, class == "Spider"),
           shade = TRUE, sub = "(Known spiders)",
           main = "Association of test group and zero results",
           xlab = "Got zero results", ylab = "Test group")
```

## Significance Testing

```{r}
# install.packages('Exact') # for exact.test
# install.packages('Barnard') # for barnardw.test
```
